Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-01-16 eacl2017.tex
New draft with all major content sections filled in

\newcommand{\figref}[2][]{Figure#1~\ref{#2}\xspace}

\title{Unsupervised acquisition of comprehensive multiword lexicons \\ using competition in an $n$-gram lattice}

@@

\section{Background and Related work}

In this paper we are attempting to identify \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized. In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas. This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalised and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational) and strong (non-compositional) MWEs. It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research. Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, come under the umbrella of FSs.

@@

\figref{fig:terminology} shows our conception of the relationship between FS, MWE and (multiword) named entities. %We use the term \termdef{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS. 
% TJB: I'd suggest staying away from talking about collocations altogether: it's an overloaded term; many MWEs are *not* collocations under this definition; and it's not needed for this paper
MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs). In this regard, we disagree with the MWE annotation schema of \newcite{Schneider14a} which includes any NE as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \ex{Tintman Nationwide Tints Ltd} or \ex{Hickory Furniture Mart} which are easily identifiable as NEs based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers.% (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names). 
% TJB: too subtle/controversial a point for this paper
The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition. Some well-known named entities are obviously good MWEs (\eg \ex{George Washington}, \ex{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.

Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen. Only some of these measures generalize beyond two words, for example PMI \cite{Church90}, the log ratio of the joint probability to the product of the marginal probabilities. Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word. The lexical predictability ratio (LPR) of Brooke et \al \cite{Brooke15b} is a association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily $n$-gram could be replaced by a single word \cite{Riedl15}.

Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb/noun combinations \cite{Fazly09}. The recent work of Schneider et \al \shortcite{Schneider14b} is a rare example of a comprehensive MWE identification model which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have be mixed \cite{Riedl16}. Otherwise, gaps in MWEs have generally addressed by using full syntactic representations \cite{Seretan11}.

Beyond association metrics, other general unsupervised approaches to the multiword unit identification include that of Newman et \al \shortcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary. Gimpel and Smith \shortcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation. The drawback to these generative methods, relative to association metrics, is scalability and lack of determinacy. Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS identification in  larger corpora, first using the conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on marginal and conditional probabilities.

%Within corpus linguistics, multiword sequences are studied with the use of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold. In order to get very reliable phrases, the threshold is typically set high enough (Biber et \al use 40 occurrences in 1 million words) to filter out the vast majority of expressions in the process. Lexical bundles generally involve larger phrasal chunks that would be missed by traditional collocation extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indiciative of particular genres (\eg university lectures).  Lexical bundles have been applied, in particular, to learner language: for example, Chen and Baker \shortcite{Chen10} showed that non-native student writers use severely a restricted range of lexical bundle types, and tend to overuse those types, while Granger and Bestgen \shortcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.

@@

The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus. Our method for FS extraction assumes such a initial set of $n$-grams, and focuses on identifying the true FS, and excluding those sequences which can be explained away due to the syntax of the language and/or the existence of other FS. The former can be captured to some extent using a syntax-sensitive association measure like LPR, but the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary.

Our approach to FS identification involves optimization of the total cost of a lattice where each node corresponds to an $n$-gram type derived from a large corpus. The cost of the whole lattice is defined simply as a product of the costs of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), with the base cost of being off simply a variation on the LPR association measure. Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}. These directional relationships allow for two basic effects between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS). A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to (non-subsuming) overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided). Given these relationships, we minimize the cost of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.

@@

The first step in the process is derive a set of $n$-grams and related statistics from a large untagged corpus of text. Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows Brooke et \al \shortcite{Brooke15b} up until the last stage. An initial requirement of any such method is a $n$-gram threshold cutoff, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \cite{Schneider14a} which indicates very good (over 90\%) type-level coverage excepting those highly particular proper names which would be better handled by a named entity recognition system. Note that our $n$-grams also include gappy versions; the definition of gaps is language specific, and we will discuss the individual languages further in section XXXXX. In general, though, putting in a restriction of this sort is important because it greatly lowers the number of gappy $n$-gram types. We also lower our number of types generally by excluding punctuation and by lemmatizing.  Note that as long as the count threshold is signifcantly above 1, efficient extraction of all $n$-grams can be done iteratively (one pass through the corpus per $n$) for both types in combination.

Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected. Again, LPR measures how statistically unlikely a particular word is relative to how predictable the word is given the same amount of syntactic context. Formally, the LPR for some word $w_i$ in the context of a sequence of words of length $n$ which have a corresponding set of sequence of POS tags $t$, is given by:

@@

These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts. We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics, not regular $n$-gram statistics.

In Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but this is not an appropriate choice here: instead, the base ``off'' cost for a node in our lattice is the minimum LPR across the words in the sequence (minLPR):

@@

For each node, there are two cost functions, one which is used if the node on ($C_{1}$), and the other if the node is off ($C_{0}$). The base value of $C_{0}$ is the minLPR metric discussed above. The base value of $C_{1}$ is a parameter to the model which, for nodes not influenced by one of the other factors discussed below, is equivalent to an initial threshold for building a vocabulary using the minLPR association measure. The lower bound on both costs is 1. There is no necessary upper bound on $C_{1}$, but we note here that there is a fairly small range of good choices for $C_{1}$; we have found that setting it too high ($>5$, corresponding to being five times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) will allow in too much random noise.

In general, we will be expanding these cost functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it. Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count. First, lets define $C_0$ as the minLPR based taken to the power of some as yet undefined function $d_0$:

\begin{displaymath}
C_0(t) = minLPR(t)^{d_0(t)}
\end{displaymath}

LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words. As such, it is common for more complex association measures to include multiplication by the count, or logarithm of the count. In the context of this model, multiplying our cost by even the logarithm of the count would be far too extreme, but we can give apply a more restricted increase to $C_0$, forcing the model to give more weight to relatively common expressions, as follows: Let $c(\dot)$ be the count function, and $c(min)$ and $c(max)$ refer to the lowest and highest count $n$-gram in the lattice (not including unigrams).

\begin{displaymath}
d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
\end{displaymath}

This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.

\begin{figure*}[!tb]
\center{\includegraphics[width=0.8\textwidth]{FS_diagram_2.pdf}}
\caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
\end{figure*}

@@

The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice. Our model includes two types of covering: hard and soft. Hard covering is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one. We do this by permanently disabling any covered node, and giving the covering node the maximum minLPR among all the nodes it covers; this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and besides being effective it also greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well. Finally, we also use hard covering to partially address the rather challenging problem of pronouns, which, due to pragmatic biases in particular corpora, often have higher than desirable LPR ratios, but cannot reasonably be excluded either since many common FS contain them. In our model, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun.

Soft covering is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to \ex{keep \gap under wraps}. We accomplish this by lowering the turned-off cost function of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\dotts_m$ be any turned-on nodes which are above $t$ in the lattice. Then, then the new $d_0$, $d_0'$ for a node $t$ is:

\begin{displaymath}
d_{0}'(t) = \frac{c(t) - \sum{c(s_1)\ldots c(s_m)}}{c(t)} d_0(t)
\end{displaymath}

>>>>

\newcommand{\figref}[2][]{Figure#1~\ref{#2}\xspace}
\newcommand{\tabref}[2][]{Table#1~\ref{#2}\xspace}
\newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}

\title{Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice}

@@

\section{Background and Related Work}

In this paper we will refer to the targets of lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon. Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FS that are shared by a recognizable language community. In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes most MWEs but also (apparently) compositional linguistic formulas. This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to even more confusion with respect to in its interpretation. Though in some contexts it has been used in way that is similar to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}}  and strong (non-compositional) MWEs. It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research. Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella. Another reason to consider a different terminology is that there are classes of what is typically considered MWE that don't fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}). Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs. Barbara W. Smith} or \ex{Smith Garden Supplies Ltd}). \figref{fig:terminology} show the conception of the relationship between FS, MWE and (multiword) named entities that we assume for this paper.

@@

%We use the term \termdef{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS. 
% TJB: I'd suggest staying away from talking about collocations altogether: it's an overloaded term; many MWEs are *not* collocations under this definition; and it's not needed for this paper
%MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs). In this regard, we disagree with the MWE annotation schema of \newcite{Schneider14a} which includes any NE as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \ex{Tintman Nationwide Tints Ltd} or \ex{Hickory Furniture Mart} which are easily identifiable as NEs based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers.% (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names). 
% TJB: too subtle/controversial a point for this paper
%The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition. Some well-known named entities are obviously good MWEs (\eg \ex{George Washington}, \ex{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.

Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word. Similarly, the lexical predictability ratio (LPR) of Brooke et \al \cite{Brooke15b} is a association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability (as provided by part-of-speech information) from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily $n$-gram could be replaced by a single word \cite{Riedl15}.

Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold. The algorithm of da Silva and Lopes \shortcite{daSilva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, appears limited \cite{Ramisch12}. Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on tradeoff between marginal and conditional statistics (\ie LPR). Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of Newman et \al \shortcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases. Gimpel and Smith \shortcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation. A general drawback to these generative methods, relative to approaching involving association metrics, is scalability and lack of determinacy.

Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb/noun combinations \cite{Fazly09}. The work of Schneider et \al \shortcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.

The motivation for building lexicons of formulaic sequences naturally overlaps of those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units (citation needed?????????), as can parsing \cite{Constant16}. One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses. Within corpus linguistics, multiword sequences have studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold: in order to get very reliable phrases, the threshold is typically set rather high (Biber et \al use 40 occurrences in 1 million words). Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures). Lexical bundles have been applied, in particular, to learner language: for example, Chen and Baker \shortcite{Chen10} showed that non-native student writers use severely a restricted range of lexical bundle types, and tend to overuse those types, while Granger and Bestgen \shortcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners. Sakaguchi et \al \shortcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; Brooke et \al \shortcite{Brooke15b} explcitly argues for FS lexicons as a way to identify, track, and improve learner proficiency.

@@

Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech combinations, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language. Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases; the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS. The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary which best explain the statistics extracted from the corpus.

%The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus. Our method for FS extraction assumes such a initial set of $n$-grams, and focuses on identifying the true FS, and excluding those sequences which can be explained away due to the syntax of the language and/or the existence of other FS. The former can be captured to some extent using a syntax-sensitive association measure like LPR, but the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary.

Our approach to FS identification involves optimization of the total cost of a lattice where each node corresponds to an $n$-gram type. The cost of the whole lattice is defined simply as a product of the costs of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and incur different costs depending on their status. Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}. These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS). A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided). Given these relationships, we minimize the cost of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.

@@

The first step in the process is derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows Brooke et \al \shortcite{Brooke15b} up until the last stage. An initial requirement of any such method is a $n$-gram frequency threshold, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of Schneider et \al \shortcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification. Note that our set of $n$-grams also include gapped or non-contiguous $n$-grams; the definition of gaps is language specific---we will discuss the gaps for individual languages further in \secref{sec:evaluation}---but the general idea (and this is confirmed by empirical analysis) is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence. In a part-of-speech tagged corpus, potential gaps can be identified by a part-of-speech regular expression. Putting in such a restriction is useful because it greatly lowers the number of gapped $n$-gram types, increasing precision and improving speed. Another way the number of types are lowered is by excluding punctuation and by lemmatizing.  Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination.

Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected. LPR measures how predictable a word is in a lexical context as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for some word $w_i$ in the context of a sequence of words of length $n$ which have a corresponding set of sequence of POS tags $t$, is given by:

@@

These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts. We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics, not regular $n$-gram statistics. Note that identification of the best ratio across all possible choices of context, not just the largest ,is important for longer FS, where the entire POS context alone might uniquely identify the phrase (and hence the word), resulting in a ratio of 1. It also ensures that the lower bound of LPR is 1, since the ratio for a word with no context at all is trivially 1.

In the segmentation approach of Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here the base ``off'' cost for a node in our lattice is the minimum LPR across the words in the sequence (minLPR):

@@

The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of minimizing the overall cost of the lattice. It is useful to define the cost of a node in terms of two cost functions. The rationale is that turning on a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to explain its existence. When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged. Let $C_{1}$ be the cost of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $C_{0}$ be the cost of a node when it off. The base value of $C_{0}$ is the minLPR metric discussed above. The base value of $C_{1}$, which we will call just $C$, is a parameter to the model which, for nodes not influenced by one of the other factors discussed below, is equivalent to an initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS. There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.

%Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count.

We will influence these cost functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it. Let's define $C_0$, then, as the minLPR based taken to the power of some as yet undefined function $d_0$:

\begin{displaymath}
C_0(t) = minLPR(t)^{d_0(t)}
\end{displaymath}
\noident

And $C_1$ is the cost parameter $C$ taken to the power of an analogous function $d_1$

\begin{displaymath}
C_1(t) = C^{d_1(t)}
\end{displaymath}
\noident

$d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes. They are also restricted to always being positive: as such, the lower bound on both costs is 1.

%LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words. As such, it is common for more complex association measures to include multiplication by the count, or logarithm of the count. In the context of this model, multiplying our cost by even the logarithm of the count would be far too extreme, but we can give apply a more restricted increase to $C_0$, forcing the model to give more weight to relatively common expressions, as follows: Let $c(\dot)$ be the count function, and $c(min)$ and $c(max)$ refer to the lowest and highest count $n$-gram in the lattice (not including unigrams).

%\begin{displaymath}
%d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
%\end{displaymath}

%This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.

\begin{figure*}[!tb]
\center{\includegraphics[width=0.8\textwidth]{FS_diagram_2.pdf}}
\caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
\label{fig:example}
\end{figure*}

@@

\subsubsection{Covering}

The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice. Our model includes two types of covering: hard and soft. \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one. We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers, (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and so it greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.  We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR ratios \cite{Brooke15b}. In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.

%Another source of error are somewhat flexible FS which fall below our $n$-gram threshold but where some portion of the FS is above the threshold: to address this, we collect additional statistics and remove as a post-processing step any FS which are hard covered by an $n$-gram not in our lattice.

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that corresponds to occurrences of \ex{keep \gap under wraps}. This is accomplished by lowering the turned-off cost function of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\dot)$ be the count function,and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, then the $d_0$ for a covered node $t$ is:

\begin{displaymath}
d_{0}(t) = \frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}
\end{displaymath}
